---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Your Name**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
covid_data_count |> 
  filter(race != "Total") |> 
  ggplot(aes(x = date, y = Deaths, color = race))+geom_smooth()
```

I saw that White as pink line is high towards other races, which mean white have highest number of death toward other race in this dataset.

2. Are there any conclusions you can draw?
White is keeping a highest number of death toward the overall race since april in this data.

3. What were you not able to do due to not having the R knowledge?
make a prediction model for people's death over cases and analyze is covid-19 becoming less harmful or more harmful to human

4. What other data would be useful to better understand this data?
overall population of each race that can help us understand the death rate and see if white also have a high death rate since some race shows low in the graph may due to small population in their race 
